### 2022-08-24 main/chapter_searches.tex
add more on decision theory, start sketching how to link to next section

\TODO{expected loss: risk}
minimize the expected risk~\cite{
wald1947bayes,
wald1950bayes,
jaynes2003probability
}
\begin{equation}
\label{eqn:searches_bayes_decision_rule}
R(t) = \int\! c(t, x) \,\mathrm{d}p(x)
,
\end{equation}
for some cost function $c(t, x)$ for decisions $t$ and states of the world
$x$ that have prior probabilities $p(x)$.
Although alternative ideas (such as minimax, minimizing a maximum
loss~\cite{savage1951review}) may empirically work well, this theory finds that
restricting oneself to Bayes decision rules cannot deny access to optimal
decisions.

>>>>

In decision theory, we want a mathematical procedure that identifies the
optimal decision to make in a given context.
Although this theory has a long history, we point specifically to the result
by Wald~\cite{
wald1947bayes,
wald1950bayes,
jaynes2003probability
}
that the optimal solution to any decision problem can be framed as the
minimization of an expected cost function, or risk:
\begin{equation}
\label{eqn:searches_bayes_decision_rule}
R(t) = \int\! c(t, x) \,\mathrm{d}p(x)
,
\end{equation}
where we mean `expected' in the mathematical mean sense of a `mean' average.
This cost function $c(t, x)$ evaluates the badness of outcomes for a given
decision $t$ and states of the world $x$ to which context must assign prior
probabilities $p(x)$.
For a given cost function and prior, one should choose the decision $t$ that
minimizes $R(t)$.

Although alternative ideas (such as minimax, minimizing a maximum
loss~\cite{savage1951review}) can empirically work well, this the mathematical
statement of this theorem states that restricting oneself to Bayes decision
rules cannot deny access to optimal decisions.
Alternatives can at best be equivalent.

This theory does not, however, define how to construct that cost function.
Like the prior, it must come from context.
Indeed the two are intertwined --- decision making machines and organisms
are capable of learning to make good decisions without constructing either
explicitly.
Towards our goal of usefully reporting data, such decision theory has been
applied to argue for ways to quote properties of posterior distributions.
For example, a minimizing the expected absolute error $|x - \check{x}$ leads to
reporting the posterior median, and minimizing the expected square error
$(x - \check{x})^2$ leads to reporting the posterior mean.
Had the rules of our bean counting game rewarded you based on such distances,
these results could have been good guesses. But those weren't the rules.

\TODO{why?
not explicitly constructed cost functions for what to report...
report for contrast with attempted alternative formulations that for social...
reasons retain popularity despite contradicting decision theory...
link to frequentist ideas
Wald worked firmly in that camp - quote
}
